Introduction

### 2021-07-12 Rmd/01_introduction.Rmd

---
title: "Introduction"
author: "Gonzalo García-Castro"
date: "3/17/2021"
output:
  word_document:
    reference_docx: trajectories_template.docx
  pdf_document:
      latex_engine: xelatex
bibliography: trajectories.bib
csl: apa6.csl
---

@@

## References

>>>>

<<<<<<< HEAD:Rmd/01_introduction.Rmd
---
title: "Introduction"
author: "Gonzalo García-Castro"
date: "3/17/2021"
output:
  word_document:
    reference_docx: trajectories_template.docx
  pdf_document:
      latex_engine: xelatex
bibliography: trajectories.bib
csl: apa6.csl
self_contained: true
---

@@
